Modalities for Location Virtualization

### 2022-09-18 semantics.tex
separted stuff
+

\section{Semantics}
\label{sec:semantics}
\mytodo{Ismail's Part}

>>>>

\section{Semantics}
\label{sec:semantics}
\subsection{Instructions}
\label{sec:instrsemantics}
The syntax of instructions is given in \fref{fig:syntax}. Their
small-step operational semantics, a~reduction relation of the form
$\hsfork{\instr}{\store}{\instr'}{\store'}{\instrs}$,
is defined in \fref{fig:semantics}.
%
The last argument~$\instrs$ is a list of newly-spawned threads;
when it is empty, we omit it
and write just $\hs{\instr}{\store}{\instr'}{\store'}$.
%
% Also, when it is a singleton, we omit the square brackets (StepFork).

% We briefly review the syntax and reduction rules.
%
The no-op ``$\iskip$'' and the sequencing construct
``$\iseq{\instr_1}{\instr_2}$'' are standard.
%

\input{fig-semantics}

### 2022-09-18 soundness.tex
+

\begin{enumerate}
\item define a certain amount of \emph{ghost state}
      that is needed in the next two steps;
\item define a central \emph{invariant}
      that ties the machine's physical state
      to the ghost state;
\item
  define the \emph{assertions} that an end user of our ... exploits, namely
  points-to assertions, deallocation witnesses, space credits, and pointed-by
  assertions; all of these assertions are defined as the ownership
  of a fragment of the ghost state.
\end{enumerate}

@@

The operational semantics of ...lang guarantees that ... (\sref{sec:valid}). A~program that attempts to ... stuck~(\sref{sec:spacelang:instructions}).
% Thus, the space consumption of every \spacelang program is bounded.
Thus, in order to prove that ... is sound, all we have to do is prove that
it rules out the possibility of a runtime failure. This is guaranteed by the
following theorem:

@@

\begin{definition}[More Terminology]
\label{def:closed}

.............
Next, we must define the relation that ties the physical store to the
\logical store, two concepts that we have informally described earlier
(\sref{sec:logical}). From here on, we write~$\store$ for the physical
store and~$\logicalstore$ for the \logical store.

\begin{definition}[Relation between Physical and \Logical Stores]
\label{def:related}
  Two stores $\store$ and $\logicalstore$ are \emph{related},
  which we write $\related\store\logicalstore$, when
  they have the same domain,
  the same reachable locations,
  and the same content at every reachable location.
\end{definition}

@@

A key Iris idiom involves the use of the \emph{authoritative
  camera}~\cite[\S6.3.3]{iris} together with an Iris invariant.
The elements of the authoritative camera include
\emph{authoritative elements} $\authfull{c}$ and
\emph{fragmentary elements} $\authfrag{b}$.
The composition law is defined in such a way that
there always exists at most one authoritative element
and the composition of all fragmentary elements in existence is
contained in the authoritative element, etc.
\end{comment}

@@

\begin{definition}[Central Invariant]
\label{def:invariant}
The central invariant of our logic,
or \emph{state interpretation invariant} \cite[\S7.3]{iris},
is the following Iris assertion:
\[
\centralinvariant\;\store \triangleq
\exists\logicalstore. \left\{
\def\arraystretch{1.2}
\begin{array}{l@{\quad\star\quad}l@{\quad}l}
  \genheapinterp\logicalstore & \star \\
   \genheapinterp\logicalstore & \star
\end{array}
\right.
\]
\end{definition}

>>>>

\begin{enumerate}
\item define a certain amount of \emph{ghost state}
      that is needed in the next two steps;
\item define a central \emph{invariant}
      that ties the machine's physical state
      to the ghost state;
\item
  define the \emph{assertions} that an end user of our ... exploits, namely
  points-to assertions that are defined as the ownership
  of a fragment of the ghost state.
\end{enumerate}

@@

The operational semantics of ...lang guarantees that ... (\sref{sec:valid}). A~program that attempts to ... stuck~(\sref{sec:instrsemantics}).
% Thus, the space consumption of every \spacelang program is bounded.
Thus, in order to prove that ... is sound, all we have to do is prove that
it rules out the possibility of a runtime failure. This is guaranteed by the
following theorem:

@@

Next, we must define the relation that ties the physical store to the
\logical store, two concepts that we have informally described earlier
(\sref{sec:logical}). From here on, we write~$\store$ for the physical
store and~$\logicalstore$ for the \logical store.

@@

A key Iris idiom involves the use of the \emph{authoritative
  camera}~\cite[\S6.3.3]{iris} together with an Iris invariant.
The elements of the authoritative camera include
\emph{authoritative elements} $\authfull{c}$ and
\emph{fragmentary elements} $\authfrag{b}$.
The composition law is defined in such a way that
there always exists at most one authoritative element
and the composition of all fragmentary elements in existence is
contained in the authoritative element, etc.
\end{comment}
% The predicate gen_heap_interp.
\newcommand{\genheapinterp}[1]{\mathit{Heap}\;#1}
% Our predicate pred (defined in ph.v), expanded.
\newcommand{\pred}[1]{\ownGhost\gammaPred{\authfull{(\mapone\predstore)}}}
% A notation for assigning fraction 1 to every element of \predstore.
\newcommand{\mapone}[1]{1.#1}
% The predicate mapsfrom_exact, expanded.
\newcommand{\mapsfromexact}[3]{
  \ownGhost\gammaPred{\authfrag{\singletonMap{#1}{(#2, #3)}}}
}
% A metavariable for a share.
\newcommand{\sh}{L'}
% The predicate mapsfrom, expanded.
\newcommand{\mapsfromdef}[3]{
  \exists\sh.\;
  \mapsfromexact{#1}{#2}{\sh} \star \pure{\sh \subseteq #3}
}

@@

\begin{definition}[Central Invariant]
\label{def:invariant}
The central invariant of our logic,
or \emph{state interpretation invariant} \cite[\S7.3]{iris},
is the following Iris assertion:
\[
\centralinvariant\;\store \triangleq
\left\{
\def\arraystretch{1.2}
\begin{array}{l@{\quad\star\quad}l@{\quad}l}
  \genheapinterp\store & \star \\
   \genheapinterp\store & \star
\end{array}
\right.
\]
\end{definition}
